---
title: "How to do a simple prediction problem using _'ridgereg()'_ function."
author: "SILA KILICOGLU (silki753@student.liu.se) and SAMI FURKAN YILDIRIM (samyi572@student.liu.se)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to do a simple prediction problem using _'ridgereg()'_ function.}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## 1. Import necessary libraries
```{r}
#library(Lab4)
library(mlbench)
library(caret)
library(leaps)
```
## 2. Split the BostonHousing data into a test and training dataset using the caret package. In this example, the proportion of training dataset to original dataset (tax data (full-value property-tax rate per USD 10,000) in boston housing) is 80%.

```{r}
set.seed(42)
data(BostonHousing)
indx <- createDataPartition(BostonHousing$tax, p = .80, list = FALSE, times = 1)  
training_set <- BostonHousing[indx,]   
test_set  <- BostonHousing[-indx,]
```

## 3. Fit a linear regression model and a fit a linear regression model with forward selection of covariates
on the training dataset.

```{r}
#Simple linear regression
fitted_lm = train(tax~., data=training_set, method="lm")
summary(fitted_lm)

#Linear regression with forward selection of covariates on the training dataset
fitted_lm_forward = train(tax~., data=training_set, method = "leapForward")
summary(fitted_lm_forward)
```

```{r}
print(fitted_lm)
```

```{r}
print(fitted_lm_forward)
```

According to the results, zn, indus, rad and medv are recommended features to use for obtaining best lm model in lm method.
```{r}
develop_fitted_lm <- train(tax ~ zn + indus + rad + medv, data = training_set, method='lm')
summary(develop_fitted_lm)
```
## 4. Evaluate the performance of this model on the training dataset.

As it can be seen below, it is obtained better result. The value of RMSE is lower in improved model than the first model and Adjusted R-squared is higher in improved model than the first model. Thus, it is improved the model by using leap forward selection, where found related features and modified the function.

```{r}
print(fitted_lm)
print(fitted_lm_forward)
print(develop_fitted_lm)
```
## 5. Fit a ridge regression model using the _"ridgereg()"_ function to the training dataset for different
values of λ.
```{r}
#ridge_model_info <- list(label= "Custom Ridge Regression Model",
#                         library = "Lab4",
#                         loop = NULL,
#                         prob = NULL,
#                         type = "Regression",
#                         parameters = data.frame(parameter = "lambda",
#                                                 class = "numeric",
#                                                 label = "Lambda"),
#                         grid = function(x, y, len=NULL, search = "grid"){
#                           data.frame(lambda = seq(0,2,by=0.25))
#                         },
#                         fit = function(x, y, wts, param, lev, last, classProbs, ...){
#                           if(is.data.frame(x)){
#                             data = x
#                             }
#                           else{
#                             data = as.data.frame(x)
#                             }
#                           data$.outcome <- y
#                           out <- Lab4::ridgereg$new(.outcome ~ ., data = data, lambda=param$lambda, ...)
#                           out
#                           },
#                         predict = function(modelFit, newdata, submodels=NULL){
#                           if(!is.data.frame(newdata)){
#                             newdata <- as.data.frame(newdata)}
#                           modelFit$predict(newdata)
#                           }
#                         )
```

```{r}
#ridge_fit <- train( tax ~ ., data=training_set, method=ridge_model_info)
#print(ridge_fit)
#plot(ridge_fit)
```
