---
title: "vignette"
author: "SILA KILICOGLU (silki753@student.liu.se) and SAMI FURKAN YILDIRIM (samyi572@student.liu.se)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## **Description**
A package to handle linear regression models with using linear algebra and RC class function.

## **Import**
```{r setup}
library(ggplot2)
library(gridExtra)
library(Lab4)
```

## **Arguments**
* _formula_
: object of class 'linreg', a symbolic description of the model to be fitted.

* _data_
: a data frame, containing the variables in the model.

## **Methods**
* _print()_
: This function print out the coefficients and coefficient names, similar as done by the lm class.

* _plot()_
: This function print out two graph ("Residuals vs Fitted" and "Scale-Location") using ggplot2.

* _resid()_
: This function print out the vector of residuals $\hat{e}$.

* _pred()_
: This function print out the predicted values $\hat{y}$.

* _coef()_
: This function print out the coefficients as a named vector.

* _summary()_
: This function print out a similar print out as printed for lm objects. It presents the coefficients with their standard error, t-value and p-value as well as the estimate of $\hat{σ}$ and the degrees of freedom in the model.

***********************
## An Example of Usage

1. Load data. Here iris dataset is used.
```r
data(iris)
```

2. Create a linear model; create an instance of the _linreg_ reference class. Here formula is _Petal.Length~Species_ and data is _iris_.

```r
mod_object = linreg(Petal.Length~Species, data = iris)
```

3. For using print function:

```r
mod_object$print()
```

4. For using plot function:

```r
mod_object$plot()
```

5. For using resid function:

```r
mod_object$resid()
```

6. For using pred function:

```r
mod_object$pred()
```

7. For using coef function:

```r
mod_object$coef()
```

8. For using summary function:

```r
mod_object$summary()
```